Chemical tagging can work: \\ Identification of stellar phase-space structures \\ purely by chemical-abundance similarity\vspace{-7ex}

### 2016-08-07 papers/kmeans/response_to_referee.txt

    There are some missing references to the original demonstrations
    of chemical tagging of unbound groups, namely the Wolf 630 group
    and HR 1614 group. Those were key to building up the case for
    this "tagging" research.

We have added the following references: De Silva et al (2007), Eggen
(1970), and Bubar & King (2010). Also Helmi et al (2006) and (2014).

    The text needs to highlight that the training set is critical -
    Cannon doesn't know physics. It needs to be told what is "true"
    and that the subsequent results will be limited to the believed
    level of truth. While it should be specified that tagging per se
    doesn't require absolute abundances, but the subsequent
    interpretation of the chemical accretion history will require
    "true" abundances - not just precision. Also some clarification
    about the Cannon's performance at the boundaries of the training
    set parameters would have been good to see.

This statement and point is true and wise. We have added a long and
substantial paragraph in Section 2 describing and emphasizing this
point, and also addressing the point that The Cannon can use
element-element correlations to improve its precision. All these
things reduce the interpretability of the absolute abundances shown in
the paper, as the referee notes. We also discuss the concern that
things could diverge at the boundaries of the training set.

We also add a paragraph in the discussion bringing up issues with
Na/Fe abundances that relate to this referee comment.

@@

    The text doesn't clarify why only k-means was chosen to do the
    'tagging' given the issues discussed, was it simply easy and
    fast? Fine as the focus of the paper is the precision of the
    abundance results with Cannon, not the fidelity of group finding.

We have added text to clarify why k-means was chosen. It is
fundamentally because k-means is the clustering algorithm of "first
resort", which contains very few assumptions and only one (integer)
adjustable parameter (not counting the metric on the vector space);
it is also well tested and understood.

    I find the group in Fig 6 dubious. Its at the very edge of the
    metallicity scale, which raises again how the Cannon performs at
    the boundaries of the training parameters. Could this not simply
    be metal-poor Halo stars, tagged as metal-poor Halo stars,
    nothing more?

The lower-right panel of Fig 6 shows that the group a strong
over-density in abundance space. The referee makes a good point: It is
indeed conceivable that this is created somehow by issues with The
Cannon at low metallicity. We now include a couple of sentences of
discussion of this point in the discussion section.  We make the
prediction for this structure that if it is followed up with data that
are sensitive to more elements, it could (in principle) be shown to
have abundances that are consistent with cluster or dwarf-galaxy
formation; if this succeeded, it might represent a discovery related
to the accretion formation of the halo.

### 2016-08-07 papers/kmeans/kmeans.tex
Szabolcs comments

HOGG: Paragraph here about limitations of \thecannon: Dependence on
training set, makes use of element-element correlations (especially, say, Na),
and delivers precision but no guarantees of accuracy beyond that in the training set.
Comment on its performance at the edges of the abundance distribution...? As per referee issue.

@@

@@

@@

\acknowledgements
It is a pleasure to thank
  Joss Bland-Hawthorn (Sydney),
  Jo Bovy (Toronto),
  Charlie Conroy (Harvard),
  Katia Cunha (\acronym{NOAO}),
  Amina Helmi (Kapteyn),
  Jeremy Magland (\acronym{SCDA}),
  Don Schneider (\acronym{PSU}),
  Keivan Stassun (Vanderbilt),
  Angus Williams (Cambridge),
  and the Blanton--Hogg group meeting
for valuable comments and discussions.
This project was funded in part by
  the \acronym{NSF} (grants \acronym{IIS-1124794}, \acronym{AST-1312863}, \acronym{AST-1517237}),
  \acronym{NASA} (grant \acronym{NNX12AI50G}),
  the Moore-Sloan Data Science Environment at \acronym{NYU}, and
  the European Research Council under the
  European Union's Seventh Framework Programme (FP~7)
  \acronym{ERC} Grant Agreement n.~\acronym{[320360, 321035]}).
This research made use of the \acronym{NASA} \project{Astrophysics Data System}.

>>>>

It is important here to note some of the limitations of stellar labels
delivered by \thecannon.
The first is that \thecannon\ is only as good as its training set!
All of the biases and calibration issues in the input training set will be
delivered to the output labels.
This means that there is no sense in which \thecannon\ delivers
absolute abundances any better than \aspcap\ does.
The second is that \thecannon\ (in the form used here) is aggressively
data-driven.
It will use anything it can to measure, say, the Na abundance, not just
actual Na lines.
This means that population-level correlations in  element abundances are
being used to deliver information about individual elements.
We bring up Na as an example here for the important reason that at low
metallicity, there are no significant Na lines in the spectra; we are
measuring Na only indirectly at low metallicity.
A third limitation of \thecannon\ is that it is operating a regression
in a very high dimensional label space.
This regression is hard to test and validate near the edges of the range
of applicability.
One way to say this is that the convex hull of the training set of
points in 17-dimensional space is potentially very small, and it is
hard to visualize what is going on outside that hull.
For these reasons, there might be label biases that grow with displacement
from the bulk of the training data.

@@

All that said, we reiterate a caveat here that we also mentioned in
\sectionname~\ref{sec:data}, which is that at very low metallicity, Na
does not show strong lines in any \apogee\ spectrum.  For this reason,
the [Na/Fe] shown for the low-metallicity structures are obtained not
by measuring Na lines but rather the lines of elements that correlate
strongly with Na at the population level.
The true [Na/Fe] may show correlations, variations, or anomalies in
the clusters that are not captured by \thecannon\ working at low
metallicity.

@@

It is conceivable that this structure, being near the outskirts of the
abundance distribution, is somehow concentrated in abundance space by
some kind of shrinkage (in the statistical sense) induced by
\thecannon's regression.
However, it is a very dense feature in abundance space, and is worth
following up.
If follow-up observations show that the stars have abundances and that
are consistent with having origin in a single stellar population or
low-metallicty dwarf galaxy, it could represent an accretion event in
the Milky Way halo.

@@

\acknowledgements
It is a pleasure to thank an anonymous referee for useful comments that have led to improvements in the manuscript.
We also thank
  Joss Bland-Hawthorn (Sydney),
  Jo Bovy (Toronto),
  Charlie Conroy (Harvard),
  Katia Cunha (\acronym{NOAO}),
  Amina Helmi (Kapteyn),
  Jeremy Magland (\acronym{SCDA}),
  Don Schneider (\acronym{PSU}),
  Keivan Stassun (Vanderbilt),
  Angus Williams (Cambridge),
  and the Blanton--Hogg group meeting
for valuable discussions and comments.
This project was funded in part by
  the \acronym{NSF} (grants \acronym{IIS-1124794}, \acronym{AST-1312863}, \acronym{AST-1517237}),
  \acronym{NASA} (grant \acronym{NNX12AI50G}),
  the Moore-Sloan Data Science Environment at \acronym{NYU}, and
  the European Research Council under the
  European Union's Seventh Framework Programme (FP~7)
  \acronym{ERC} Grant Agreement n.~\acronym{[320360, 321035]}).
This research made use of the \acronym{NASA} \project{Astrophysics Data System}.
